Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-05-30 neurips-20/cvx-flats.tex
comments on 2,3

\bo{Citation help appreciated!}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
We would like to be able to lower-bound this dimension for a given learning problem.
\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky. Then the bullet points explain the different settings.}
But consistency, which we formalize in Section \ref{sec::consis-implies-indir}, is not very tractable.
Ideally, we would have a more useful condition that could apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$

@@

For discrete prediction problems, one often is able to intuitively start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for rankings, a borda-like loss that assigns error based on one's distance from the winner's predicted ranking.
However, when one starts with a (often discrete) target loss they want to minimize, it is often a computationally hard problem.
For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.

@@

\subsection{Property elicitation}\label{subsec:properties}
In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is a necessary condition for constructing a consistent surrogate loss.
Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
Recently, the elicitation of multiple properties simultaneously and of high-dimensional properties was studied by~\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to indirectly elicit (see Definition~\ref{def:indirectly-elicits} below) a property or vector of properties by directly eliciting other (possibly vector-valued) properties.
Moreover,~\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss.

@@

\subsection{Complexity notions}\label{subsec:complexity}
\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
However, we show that our Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.

@@

When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
\begin{definition}[Convex Elicitation Complexity]
	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
\end{definition}

We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits when we are in a finite prediction setting.
\begin{proposition}
	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
\end{proposition}
\begin{proof}
	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.\jessiet{Ordering of this? Also don't love having a Proposition in Section 2}
\end{proof}

\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of calibration.
Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
It is an open problem to understand if these efficiency definitions are generally equivalent. \jessiet{Move this sentence to conclusions?  It's currently in both.}

@@

\jessie{Mention calibration results are in the appendix if the reader wants that connection too.}
\paragraph{Our approach: indirect elicitation.}
In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings.
This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}), so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
Yet it gives state-of-the-art lower bounds on $d$.
In particular, indirect-elicitation bounds imply feasible subspace dimension bounds.

To begin, we formalize consistency in two ways.
First (Definition \ref{def:consistent-ell}), if one is given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$.
Second (Definition \ref{def:consistent-prop}), if one is given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some measurable sense, the correct statistic $\gamma(D_x)$ of the conditional distributions.
We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}
\bo{On the right side, is measurable enough? I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$. Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}

>>>>

\bo{Citation help appreciated!}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
\raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
We would like to be able to lower-bound this dimension for a given learning problem.
\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky. Then the bullet points explain the different settings.}
But consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
Ideally, we would have a more useful condition that could apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$

@@

\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}
For discrete prediction problems, one often is able to intuitively start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for rankings, a borda-like loss that assigns error based on one's distance from the winner's predicted ranking.
\raft{``Borda'', and anyway ML folks probably won't know what you mean}
However, when one starts with a (often discrete) target loss they want to minimize, it is often a computationally hard problem.
For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.

@@

\subsection{Property elicitation}\label{subsec:properties}
In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is a necessary condition for constructing a consistent surrogate loss.
\raft{Would suggest going straight to the next paragraph from here.  Some of this could merge with discussion later in this subsection, and the rest in ``complexity''.}
Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
Recently, the elicitation of multiple properties simultaneously and of high-dimensional properties was studied by~\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}.
In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to indirectly elicit (see Definition~\ref{def:indirectly-elicits} below) a property or vector of properties by directly eliciting other (possibly vector-valued) properties.
Moreover,~\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss.

@@

\subsection{Complexity notions}\label{subsec:complexity}

\raf{I'd start off by motivating / explaining what all of these notions are trying to do, and perhaps fold in some related work discussion from above.  Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}
\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
However, we show that our Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.

@@

When $\R \subseteq \reals^d$ for some $d \in \mathbb{Z}$\raf{N not Z}, \cite{frongillo2018elicitation} similarly introduce the notion of \emph{(convex) elicitation complexity}, which uses $d$ to measure the ``efficiency'' of a loss $L$ eliciting $\Gamma$.
\raft{If you motivate above, you can kill the ``efficiency'' bit and be more precise here about the difference wrt ccdim}
However, their notion of complexity relies not just on the property $\Gamma$, but instead on any property \emph{indirectly elicited} by $L$.
\raft{Didn't follow this last sentence}
\begin{definition}[Convex Elicitation Complexity]
	The \emph{convex elicitation complexity} of a property $\eliccvx(\Gamma)$ is the minimum dimension $d$ such that there is a convex loss $L : \reals^d \times \Y \to \reals$ indirectly eliciting $\Gamma$.
\end{definition}

We can additionally relate convex calibration dimension of a loss to the convex elicitation complexity of the loss it elicits when we are in a finite prediction setting.
\begin{proposition}
	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
\end{proposition}
\begin{proof}
	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.\jessiet{Ordering of this? Also don't love having a Proposition in Section 2}
  \raft{I'd suggest explaining why this is true in text, and ref the appendix where we discuss in more detail}
\end{proof}

\raf{It makes sense to discuss this here, but be a bit more precise with how they relate.  E.g. embedding is actually a special case of indirect elicitation.  You can say we show that calibration and indirect elic are equivalent for polyhedral losses, in the sense that if a polyhedral loss indirectly elicits a discrete loss, it is calibrated wrt that loss.  But we don't know exactly how ``convex elic complex'', ``embedding dimension'', ``polyhedral calibration dimension'', and ccdim relate.  Try to spell it out carefully, but briefly :-).  If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}
\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of calibration.
Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of finite properties and convex calibration dimension of discrete losses.
It is an open problem to understand if these efficiency definitions are generally equivalent. \jessiet{Move this sentence to conclusions?  It's currently in both.}

@@

In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings.
This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}),
\raft{I really like the flow here, but was thinking of a slightly longer version of the nod to calibration.  Like ``You may be wondering if we could leverage ``consistency $\iff$ calibration'' to prove this.  We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.  We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''}
so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
Yet it gives state-of-the-art lower bounds on $d$.
In particular, indirect-elicitation bounds imply feasible subspace dimension bounds.

To begin, we formalize consistency in two ways.
First, if one is given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
Second, if one is given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}
\botodo{On the right side, is measurable enough? I guess we need $\psi \circ f$ to be measurable...on the other hand, we don't want to constrain $f$ based on $\psi$. Do we need a condition on $\psi$ that guarantees $\psi \circ f$ is measurable?}
\raft{I think okay as written -- if $\psi$ is restrictive, you won't achieve consistency.  And typically $f$ is much more expressive anyway, e.g. $\reals^\Y$ for classification.}
